Sustainable computational science:\\ the ReScience initiative

### 2017-07-24 affiliations.tex
PDF build
Minor affiliation correction for Thomas Arildsen

$^{3}$Department of Electronic Systems, Faculty of Engineering and Science, Aalborg University, Denmark

@@

$^{9}$IGBMC, INSERM U964, CNRS UMR 7104, Université de Strasbourg, Illkirch, France

>>>>

$^{3}$Department of Electronic Systems, Technical Faculty of IT and Design, Aalborg University, Denmark

@@

$^{9}$Institut de Génétique et de Biologie Moléculaire et Cellulaire, INSERM U964, CNRS UMR 7104, Université de Strasbourg, Illkirch, France
